The Rethink Robotics Sawyer manipulator retails for \$29,000 \cite{rr}. The Prescott Embry-Riddle robotics lab has 1 and the University's average student pays \$35,654 annually -- after financial aid \cite{ff}. Further, \$25,000 to \$35,000 is a common price for manipulators with a reach of approximately 1 meter and payload capacity below 1 kg \cite{gg}. While Trossen Robotics offers low cost manipulators between one sixth and one sixtieth of Sawyer’s cost, for accuracy of 1mm, the cost is still around \$2,000. For secondary education institutions, robotics is cost prohibitive. Consequently, students have less opportunities in high school to learn about robotics. The Manipulator for Educational Institutions with Open Source Integrated Systems (MEIOSIS) aims to increase the accessibility of robotics education to secondary education institutions and hobbyists.

In biology, meiosis is a process of cell division similar to mitosis. However, unlike mitosis, the resulting daughter cells are used to create new life during sexual recombination. Meiosis occurs in two sets of cell division: meiosis I and meiosis II. Analogously, MEIOSIS has a Preliminary and Detail semester. During meiosis I, chromosomes pair up and swap genetic material (DNA) in preparation for cell division. Then, during meiosis II, the parent cell splits into two haploids, which each split into two gametes. The gamete cells have half the number of chromosomes compared to a cell produced by mitosis and are not identical to their parent cell. When combined with another gamete, a new, unique cell emerges. MEIOSIS does not change the DNA of robotics. However, in combining with user needs and incorporating innovative design elements, MEIOSIS brings new life to robotics education.

This document outlines MEIOSIS’s solution for increasing the accessibility of robotics education, current project status, and plans for the Detail semester. Specifically, it is subdivided into four sections: Requirements, Conceptual Design, Specifications, and Preliminary Design. The Preliminary Design comprises the majority of the document. It explains the evolution of MEIOSIS’s manipulator, noting design decisions and changes made from simulations, tested parts, and motor calculations. Finally, an appendix contains simulation code and drawings for all parts.
