\emph{Table \ref{tab:bom1}} lists the parts MEIOSIS will require to build the manipulator. The total cost is \$629.22, including shipping. Specification 1.1b requires MEIOSOS’s cost to develop the manipulator be less than \$800. In addition to pulley belts for the current configuration, \emph{Table \ref{tab:bom1}} allocates \$20 for two additional belt sizes to increase joint 1/2’s and joint 3’s torque by a factor of 10. The belts must be purchased in packs of 3 from Automation Direct and two more belt sizes may be required for the two pulley design to allow the servos to be mounted without interfering with the base. \emph{Table \ref{tab:bom1}} also accounts for increased cable lengths of 500 mm to communication bus signals from motor 2 to 3 and motor 3 to 4. And cable lengths of 350 mm to communication bus signals from motor 5 to 6. Motors are identified in [MOTOR ORIENTATION FIGURE]. Aside from electronic hardware, \emph{Table \ref{tab:bom2}} for physical hardware.
To allow screw mounting in plastic with metal threads, \emph{Table \ref{tab:bom2}} accounts for 100 threaded press-fit inserts. The manipulator will require between 21 and 46 inserts.The majority of inserts attach MX-12W servos to the manipulator. Mounting hardware accompanies each servo. Since purchasing six sets of pulleys would put MEIOSIS over the \$800 budget, they are printed.
\renewcommand{\arraystretch}{1.15}
\begin{table}[htp]
  \center
  \caption{MEIOSIS Bill of Materials with Costs}
  \label{tab:bom1}
\begin{tabular}{cC{3cm}@{\hskip 3pt}c@{\hskip 3pt}C{3cm}@{\hskip 3pt}|C{3cm}}
\multirow{2}{*}{\textbf{Part}} & \multirow{2}{*}{\textbf{Retailer}} & \multirow{2}{*}{\textbf{Quantity}} & \textbf{Unit Cost (USD)} & \textbf{Total Cost (USD)} \\\hline
3 pack, 300 tooth & \multirow{4}{*}{\shortstack[c]{Automation \\Direct}} & 1 & 11.5 & 11.5 \\
3 pack, 208 tooth &  & 1 & 9.5 & 28.5 \\
Base second belts &   & 1 & 10 & 10 \\
Link 3 second belts & & 1 & 10 & 10 \\\arrayrulecolor{gray}\hline
MX-12W & \multirow{4}{*}{\shortstack[c]{Trossen \\Robotics}} & 6 & 65.9 & 395.4 \\
500 mm, 1/2 pulleys &  & 2 & 3.95 & 7.9 \\
350 mm, 3 pulley &  & 1 & 2.95 & 2.95 \\
EE &  & 1 & 24.95 & 24.95 \\\arrayrulecolor{gray}\hline
Pi 3 B & \multirow{2}{*}{Amazon} & 1 & 37.99 & 37.99 \\
Bearings &  & 1 & 8.99 & 8.99 \\\arrayrulecolor{gray}\hline
\multirow{2}{*}{2 Sch 10 12" Al tube} & Industrial Metal Sales & 1 & 2.99 & 2.99 \\\arrayrulecolor{gray}\hline
\multirow{2}{*}{12 V, 5 V power supply} & Digi-Key Electronics & 1 & 43.21 & 43.21 \\\arrayrulecolor{gray}\hline
Automation Direct & \multirow{5}{*}{Shipping} & \multirow{5}{*}{---} & \multirow{5}{*}{---} & 0 \\
Trossen Robotics &  &  & & 13.15 \\
Amazon & &  & & 0 \\
Industrial Metal Sales &  & &  & 26.36 \\
Digi-Key &  & &  & 8.99 \\
& & & \textbf{Total} & 629.22 \\
\end{tabular}
\end{table}

In addition to the costs listed in \emph{Table \ref{tab:bom1}}, \emph{Table \ref{tab:bom2}} shows further costs for the end-user highlighted in blue. Since the Embry Riddle robotics lab has 3D printing available without affecting MEIOSIS’s \$800 budget, \emph{Table \ref{tab:bom2}} accounts for outsourced 3D printing costs sufficient to print the entire manipulator with six sets of pulleys. If the end-user owns a 3D printer, the 3D printing cost would effectively reduce to filament cost. Additionally, \emph{Table \ref{tab:bom2}} assumes the end-user does not already possess an AX-12A servo to be used with the end-effector. Further, \emph{Table \ref{tab:bom2}} assumes the manipulator would be more accessible to end-users by using a proprietary U2D2 communication module in lieu of a soldered or bread-board circuit.
The robotics lab has an AX-12A servo and U2D2 communication module MEIOSIS will use. With the aforementioned additional costs, the MEIOSIS manipulator costs the end-user  \$1,007.98 including shipping costs. While \$1,007.98 is slightly above the maximum cost of \$1000 from specification 1.1a, it provides greater accessibility, which may be diminished by assuming end-users poses 3D printers.

\renewcommand{\arraystretch}{1.25}
\begin{table}[htp]
  \center
  \caption{End-User Bill of Materials with Costs}
  \label{tab:bom2}
  \begin{tabular}{C{3cm}C{3cm}@{\hskip 3pt}c@{\hskip 3pt}C{3cm}@{\hskip 3pt}|C{3cm}}
  \multirow{2}{*}{\textbf{Part}} & \multirow{2}{*}{\textbf{Retailer}} & \multirow{2}{*}{\textbf{Quantity}} & \textbf{Unit Cost (USD)} & \textbf{Total Cost (USD)} \\\hline
  Aforementioned Costs & \multirow{2}{*}{\emph{Table \ref{tab:bom1}}} & \multirow{2}{*}{---} & \multirow{2}{*}{---} & 629.22 \\
  \multirow{2}{*}{U2D2} & Trossen Robotics & \multirow{2}{*}{1} & \multirow{2}{*}{49.9} & \multirow{2}{*}{49.9}\\
  \multirow{2}{*}{EE with servo} & Trossen Robotics & \multirow{2}{*}{1} & \multirow{2}{*}{64.95} & \multirow{2}{*}{64.95} \\
  3D PLA outsourcing (incl. shipping) & \multirow{2}{*}{Craft Cloud} & \multirow{2}{*}{1} & \multirow{2}{*}{288.86} & \multirow{2}{*}{288.86} \\
  & & & \textbf{Total} & 1007.98 \\
  \end{tabular}
\end{table}
\renewcommand{\arraystretch}{1}
\newpage
