\hiddensubsection{Hardware}
The following requirements are hardware specific and dictate the physical constraints the system must adhere to.
\subsubsection{The system shall cost the end-user no more than \$1000.}
\subsubsection{The system shall be fully dexterous without being kinematically redundant.}
To create a system with the intention of advancing education, it must be complex enough to encourage higher level problem solving, as well as be capable enough (dexterous) in a broad spectrum of tasks — in the interest of remaining useful in addition to retaining the interest of students.

\subsubsection{The system end effector shall maintain a positional accuracy magnitude of \(\pm 1\) mm and an orientation accuracy of \(\pm 5^{\circ}\) eigen angle from the base frame.}
To ensure that the robot has educational value, the accuracy must be defined so that any desired positions and movements are achieved.

\subsubsection{The system end effector shall maintain a pose repeatability magnitude between 0.1—1.5 mm for the position and \(\pm 4^{\circ}\) eigen angle from the base frame for the orientation.}
This is to ensure a robot that can execute the same movement commands repeatedly and have the same results every time.

\subsubsection{The system’s reachable workspace shall be a hemisphere with a radius of 300-700 mm.}
This workspace will provide enough movement to manipulate objects in order to perform basic tasks.

\subsubsection{The system’s dexterous workspace shall contain a hemispherical shell within the reachable workspace with a thickness of 280 mm.}

\subsubsection{The system shall have a removable end effector capable of picking and placing a low-odor chisel tip Expo dry erase marker.}
This creates a robot capable of performing a variety of basic tasks, which enhances its educational value.

\subsubsection{The system shall be able to write with a low-odor chisel tip Expo dry erase marker.}

\hiddensubsection{Software}
\subsubsection{The system shall be open source.}
This will create an easily obtainable, low cost method of distributing the system’s source code, which may be modified for personal use.

\subsubsection{The system shall be capable of operating given only desired end effector cartesian coordinates specified with respect to the base frame.}
This simplicity makes the system of use to inexperienced users.
